Thermodynamic fragments in magic state theories

### 2021-01-13 magic_paper.tex
added calculations on a first bound, looks very loose though, not complete

The first elbow of the target state is located at $x'_0 = \frac{1}{9^{\tt}} > x_\star$, so in order to find the target state Lorenz curve coordinate $L'_\star$ at location $x_\star$, we can interpolate between the origin and the first target state elbow, 
\begin{equation}
	\begin{split}
	L'_\star &= \frac{x_\star}{x'_0}L'_0 = \frac{1}{9^{\nn-\tt}}\left( \frac{5}{3} - \frac{8}{9}\epsilon'\ \right)^{\tt}\Phi_+\left(0;\tt,\frac{12-4\epsilon'}{15-8\epsilon'}\right) \\
	&= \frac{(3-4\epsilon')^{\tt}}{9^{\nn}}.
	\end{split}
\end{equation}
The process in~\cref{eq:sudist} is therefore possible only if $L_\star \geq L'_\star$ or equivalently,
\begin{align}
	\frac{n}{n'} &\geq \frac{\ln{(3-4\epsilon')}}{\ln{(3-4\epsilon)}}, \text{ or}\\
	\epsilon &\leq \frac{3}{4} - \frac{1}{4}(3-4\epsilon')^{\frac{\tt}{\nn}}.
\end{align}
As an example, the process with $(\nn, \tt) = (12, 4)$ and $\epsilon' = 0.05$ yields $\epsilon \leq 0.398$.
Numerical comparison of the curves with varying $\epsilon$ suggests that we require $\epsilon \leq 0.373$ for the process to be possible.

@@

Consider a general qutrit Hamiltonian $H$ with spectrum $(E_0, E_1, E_2)$.
The Wigner distribution of any qutrit thermal state $\gamma_\beta$ is calculated directly by the definition in~\cref{eq:wstate},
\begin{equation}
	\W[\bmx]{\gamma_\beta} = \frac{e^{-\beta E_{x_0}}}{d\Z_\beta}\ \text{for all}\ \bmx \in \pd,
\end{equation}
and always consists of strictly positive components, therefore the pre-order $\prec_{\gamma_\beta}$ is well defined.

Consider the simple scenario, where $H$ has the spectrum $(1,0,0)$.
Then, $\Z_\beta = 2 + e^{-\beta}$ and the 1-copy Wigner distributions are depicted in~\cref{tab:thermal_w}.
\begin{table}[h]
  \def\arraystretch{2}
  \centering
  \begin{tabular}{c|c|c|c}
    $\bmx = (x_0, x_1)$ & $W_{\noisys}(\bmx)$ & $W_{\gamma_\beta}(\bmx)$ & $W_{\noisys}(\bmx)/W_{\gamma_\beta}(\bmx)$ \\
    \hline
    \makecell{$(0,0)$ \\ \vdots \\ $(0,2)$} & $\displaystyle \frac{1}{6} - \frac{1}{18}\epsilon$ & $\displaystyle \frac{1}{3(1+2e^\beta)}$ & $\displaystyle \left(\frac{1}{2}-\frac{1}{6}\epsilon \right)(1+2e^\beta)$ \\
    \hline
    \makecell{$(1,0)$ \\ $\vdots$ \\ $(2,1)$} & $\displaystyle \frac{1}{6} - \frac{1}{18}\epsilon$ & $\displaystyle \frac{1}{3(2+e^{ -\beta})}$ & $\displaystyle \left(\frac{1}{2}-\frac{1}{6}\epsilon \right)(2+e^{-\beta})$ \\
    \hline
    $(2,2)$ & $\displaystyle -\frac{1}{3} + \frac{4}{9}\epsilon$ & $\displaystyle \frac{1}{3(2+e^{-\beta})}$ & $\displaystyle \left(-1 + \frac{4}{3}\epsilon \right)(2+e^{-\beta})$ \\
    \hline
  \end{tabular}
  \caption{Wigner components $W_{\gamma_\beta}(\bmx)$, $W_{\noisys}(\bmx)$ and their ratio $W_{\noisys}(\bmx)/W_{\gamma_\beta}(\bmx)$ listed in order of decreasing ratio (holds for all $\beta$).}
  \label{tab:thermal_w}
\end{table}
To construct the Lorenz curves, we simply take the cumulative sum of the Wigner components in order of increasing ratio.

>>>>

The first elbow of the target state is located at $x'_0 = \frac{1}{9^{\tt}} > x_\star$, so in order to find the target state Lorenz curve coordinate $L'_\star$ at location $x_\star$, we can interpolate between the origin and the first target state elbow, 
\begin{equation}\label{eq:constraint_deriv}
	\begin{split}
	L'_\star &= \frac{x_\star}{x'_0}L'_0 = \frac{1}{9^{\nn-\tt}}\left( \frac{5}{3} - \frac{8}{9}\epsilon'\ \right)^{\tt}\Phi_+\left(0;\tt,\frac{12-4\epsilon'}{15-8\epsilon'}\right) \\
	&= \frac{(3-4\epsilon')^{\tt}}{9^{\nn}}.
	\end{split}
\end{equation}
The process in~\cref{eq:sudist} is therefore possible only if $L_\star \geq L'_\star$ or equivalently,
\begin{align}
	\frac{n}{n'} &\geq \frac{\ln{(3-4\epsilon')}}{\ln{(3-4\epsilon)}}, \text{ or}\\
	\epsilon &\leq \frac{3}{4} - \frac{1}{4}(3-4\epsilon')^{\frac{\tt}{\nn}}.
\end{align}
As an example, the process with $(\nn, \tt) = (12, 4)$ and $\epsilon' = 0.05$ yields $\epsilon \leq 0.398$.
Numerical comparison of the curves with varying $\epsilon$ suggests that we require $\epsilon \leq 0.373$ for the process to be possible.

@@

Consider a general qutrit Hamiltonian 
\begin{equation}
	H = E_0 \ketbra{0} + E_1 \ketbra{1} + E_2 \ketbra{2},
\end{equation}
where the eigenbasis coincides with the computation basis of the Pauli Z operator.
The Wigner distribution of any qutrit thermal state $\gamma_\beta$ is calculated directly by the definition in~\cref{eq:wstate},
\begin{equation}
	\W[\bmx]{\gamma_\beta} = \frac{e^{-\beta E_{x_0}}}{d\Z_\beta}\ \text{for all}\ \bmx \in \pd,
\end{equation}
and always consists of strictly positive components, therefore the pre-order $\prec_{\gamma_\beta}$ is well defined.

Consider the simple scenario, where $H$ has the spectrum 
\begin{equation}
	(E_0, E_1, E_2) = (1,0,0).
\end{equation}
Then, $\Z_\beta = 2 + e^{-\beta}$ and the 1-copy Wigner distributions are depicted in~\cref{tab:thermal_w}.
\begin{table}[h]
  \def\arraystretch{2}
  \centering
  \begin{tabular}{c|c|c|c}
    $\bmx = (x_0, x_1)$ & $W_{\noisys}(\bmx)$ & $W_{\gamma_\beta}(\bmx)$ & $W_{\noisys(\epsilon)}(\bmx)/W_{\gamma_\beta}(\bmx)$ \\
    \hline
    \makecell{$(0,0)$ \\ \vdots \\ $(0,2)$} & $\displaystyle \frac{1}{6} - \frac{1}{18}\epsilon$ & $\displaystyle \frac{1}{3(1+2e^\beta)}$ & $\displaystyle \left(\frac{1}{2}-\frac{1}{6}\epsilon \right)(1+2e^\beta)$ \\
    \hline
    \makecell{$(1,0)$ \\ $\vdots$ \\ $(2,1)$} & $\displaystyle \frac{1}{6} - \frac{1}{18}\epsilon$ & $\displaystyle \frac{1}{3(2+e^{ -\beta})}$ & $\displaystyle \left(\frac{1}{2}-\frac{1}{6}\epsilon \right)(2+e^{-\beta})$ \\
    \hline
    $(2,2)$ & $\displaystyle -\frac{1}{3} + \frac{4}{9}\epsilon$ & $\displaystyle \frac{1}{3(2+e^{-\beta})}$ & $\displaystyle \left(-1 + \frac{4}{3}\epsilon \right)(2+e^{-\beta})$ \\
    \hline
  \end{tabular}
  \caption{Wigner components $W_{\gamma_\beta}(\bmx)$, $W_{\noisys}(\bmx)$ and the associated slope $W_{\noisys}(\bmx)/W_{\gamma_\beta}(\bmx)$ listed in order of decreasing slope (holds for all $\beta$).}
  \label{tab:thermal_w}
\end{table}

To construct the 1-copy Lorenz curve $\lc{\noisys(\epsilon)}{\gamma_\beta}$, we simply take the cumulative sum of the Wigner components in order of decreasing slope $W_{\noisys}(\bmx)/W_{\gamma_\beta}(\bmx)$.
The first elbow of the 1-copy Lorenz curve is
\begin{equation}
	(x_0, L_0) = \left( \frac{1}{1+2e^\beta}, \frac{1}{2} - \frac{1}{6}\epsilon \right).
\end{equation}

In order to construct the 2-copy Lorenz curve, we first obtain the 2-copy Wigner distribution as a convolution of the 1-copy Wigner distribution (between two identical systems A and B) and then take again the cumulative sum of the Wigner components in order of decreasing slope $W_{\noisys\too{2}}(\bmx_A \oplus \bmx_B)/W_{\gamma_\beta\too{2}}(\bmx_A \oplus \bmx_B)$.
This order, hence the first elbow depends on the temperature,
\begin{equation}
	(x_0, L_0) = 
	\begin{cases}
		\left( \frac{1}{9(2+e^{-\beta})^2}, \left(\frac{1}{3} - \frac{4}{9}\epsilon \right)^2 \right),\ &\beta \leq \ln{\left(8-\frac{18}{3-\epsilon}\right)}, \\
		\left( \frac{1}{(1+2e^\beta)^2}, \left(\frac{1}{2} - \frac{1}{6}\epsilon \right)^2 \right),\ &\beta \geq \ln{\left(8-\frac{18}{3-\epsilon}\right)}.
	\end{cases}
\end{equation}

\nick{Unfortunately, performing the same calculation as in~\cref{eq:constraint_deriv} for $\beta \leq \ln{\left(8-\frac{18}{3-\epsilon}\right)}$, yields a very loose bound.
The first elbow is not a good indicator in this case, points closer to the peak intersect first.}
